---
title: "Compare covid19 in Australia and Canada"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Compare covid19 in Australia and Canada}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(covidpkg)
```

### How to launch the app

This app can be lauched just by typing "launch_app()" in your console.

### What the app does

This app contains a table, a plotly gragh and a dygragh.  
A dygragh based on comparing the number of cases and deaths in Australia and Canada from 1st March 2020 to 7th October 2020.    
A plotly graph focus on comparing the everyday new cases from March to May for analysing the COVID19 in this two countries at the beginning of the epidemic.   
Tables with selected data range and plots with selected country can be changed from users.  

### Guidelines

You can install the released version of covidpkg from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("covidpkg")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("etc5523-2020/r-package-assessment-YuqiWang517")
```